---
title: "parental_buffer_behav_analyses"
author: "Lior Abramson"
date: "August 2022"
output: html_document
---

House keeping:
```{r setup, include=FALSE}
#cleaning the environment
  rm(list = ls())
  cat ("\014")
  if(is.null(dev.list()) == FALSE) dev.off()

#Packages
  packages <- c('reshape','psych','rstatix','tidyverse', 'Rmisc', 'lme4')
  lapply(packages, require, character.only = TRUE)

```

Load data:
```{r}
#load data
  D <- read.csv("../data/Class_cond_Behav_all_030422.csv")
```

Organize data:
```{r}
#arrange response vars (like+nervous questions)
  DBehav <-D[!is.na(D$LikePre.RESP)|!is.na(D$LikePost.RESP),] #take only rating trials
  
  DBehav$Like.RESP <- NA
  DBehav$Like.RESP[!is.na(DBehav$LikePre.RESP)]  <- DBehav$LikePre.RESP[!is.na(DBehav$LikePre.RESP)] 
  DBehav$Like.RESP[!is.na(DBehav$LikePost.RESP)] <- DBehav$LikePost.RESP[!is.na(DBehav$LikePost.RESP)]
  
  DBehav$Nervous.RESP <- NA
  DBehav$Nervous.RESP[!is.na(DBehav$NervousPre.RESP)]  <- DBehav$NervousPre.RESP[!is.na(DBehav$NervousPre.RESP)] 
  DBehav$Nervous.RESP[!is.na(DBehav$NervousPost.RESP)] <- DBehav$NervousPost.RESP[!is.na(DBehav$NervousPost.RESP)]

  DBehav$time <- NA
  DBehav$time[!is.na(DBehav$LikePre.RESP)]  <-"Pre"
  DBehav$time[!is.na(DBehav$LikePost.RESP)] <-"Post"
  DBehav$version_time_and_stim <- paste0(DBehav$Version,"_",DBehav$time,"_",DBehav$Shape)
  
#take only relevant vars  
  DBehav <- DBehav[,c("Subject","DataFile.Basename","Like.RESP","Nervous.RESP","version_time_and_stim")]
  
#remove version V1_REG of subject EL062  (a redundant, wrong file) 
  DBehav <- DBehav[!(DBehav$Subject==62 & DBehav$DataFile.Basename=="Class_cond_v1_REG-0062-1"),]

```

combine information about condition (parent/alone)
```{r}
#turn to wide format
#ignore warning message (refers to a subject who is about to be removed from the file anyway)
  DBehav_Wide <- reshape(DBehav, timevar="version_time_and_stim",idvar="Subject", direction="wide")

#import condition data
  DParentInfo <- read.csv("../data/ClassCond_ParentConditionData.csv")
  DBehav_Wide <- merge(DBehav_Wide,DParentInfo[,c("Subject","Version_Parent","Version_Alone")], by="Subject", all.x=T, all.y=F)
  
```

check demographic details:
```{r}
#import data
  DDemographics <- read.csv("../data/ELFK_demographics.csv")
  DBehav_Wide <- merge(DBehav_Wide,DDemographics[,c("Subject","SEX","MRI_AGE","DEM_4_RACE_CHILD","DEM_4_RACE_CHILD_OTHER")], by="Subject", all.x=T, all.y=F)
  
#check demographic details
  #age
  summary(DBehav_Wide$MRI_AGE) 
  sd(DBehav_Wide$MRI_AGE, na.rm=T) 
  #sex
  summary(as.factor(DBehav_Wide$SEX))
  #race
  summary(as.factor(DBehav_Wide$DEM_4_RACE_CHILD))
```

exclude participants (from both long and wide dataframes)
```{r}
#remove subjects 76 and 80 (experimenter error- watched the same shapes in both parent and alone condition)
#remove subjects 24 and 88 (did not complete both conditions)
  DBehav <- DBehav[DBehav$Subject!=76 & DBehav$Subject!=80 & DBehav$Subject!=24 & DBehav$Subject!=88,]
  DBehav_Wide <- DBehav_Wide[DBehav_Wide$Subject!=76 & DBehav_Wide$Subject!=80 & DBehav_Wide$Subject!=24 & DBehav_Wide$Subject!=88,]

#remove children from the caregiving related early adversities group
  crEAsgroup <-c("6","60","97","98","99","101","102")
  for (i in crEAsgroup){DBehav <- DBehav[DBehav$Subject!=i,]}
  for (i in crEAsgroup){DBehav_Wide <- DBehav_Wide[DBehav_Wide$Subject!=i,]}
  
#check age, sex and race for the final behavioral sample
  #age
  summary(DBehav_Wide$MRI_AGE) 
  sd(DBehav_Wide$MRI_AGE, na.rm=T) 
  #sex
  summary(as.factor(DBehav_Wide$SEX))
  #race
  summary(as.factor(DBehav_Wide$DEM_4_RACE_CHILD))
  
```

create raw scores for each condition in the wide format
```{r}
#like question
  DBehav_Wide$ParentPre_CSPlus <- NA
  DBehav_Wide$ParentPre_CSMinus <- NA
  DBehav_Wide$AlonePre_CSPlus <- NA
  DBehav_Wide$AlonePre_CSMinus <- NA
  
  DBehav_Wide$ParentPost_CSPlus <- NA
  DBehav_Wide$ParentPost_CSMinus <- NA
  DBehav_Wide$AlonePost_CSPlus <- NA
  DBehav_Wide$AlonePost_CSMinus <- NA
  
  DBehav_Wide$ParentPre_CSPlus[DBehav_Wide$Version_Parent=="V1"]   <-DBehav_Wide$Like.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSPlus[DBehav_Wide$Version_Parent=="V2"]   <-DBehav_Wide$Like.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPre_CSMinus[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Like.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSMinus[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Like.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSPlus[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Like.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSPlus[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Like.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSMinus[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$Like.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSMinus[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$Like.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$AlonePre_CSPlus[DBehav_Wide$Version_Alone=="V1"]   <-DBehav_Wide$Like.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSPlus[DBehav_Wide$Version_Alone=="V2"]   <-DBehav_Wide$Like.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePre_CSMinus[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Like.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSMinus[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Like.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSPlus[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Like.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSPlus[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Like.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSMinus[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$Like.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSMinus[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$Like.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Alone=="V2"] 
  
#nervous question
  DBehav_Wide$ParentPre_CSPlus.ner <- NA
  DBehav_Wide$ParentPre_CSMinus.ner <- NA
  DBehav_Wide$AlonePre_CSPlus.ner <- NA
  DBehav_Wide$AlonePre_CSMinus.ner <- NA
  
  DBehav_Wide$ParentPost_CSPlus.ner <- NA
  DBehav_Wide$ParentPost_CSMinus.ner <- NA
  DBehav_Wide$AlonePost_CSPlus.ner <- NA
  DBehav_Wide$AlonePost_CSMinus.ner <- NA
  
  DBehav_Wide$ParentPre_CSPlus.ner[DBehav_Wide$Version_Parent=="V1"]   <-DBehav_Wide$Nervous.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSPlus.ner[DBehav_Wide$Version_Parent=="V2"]   <-DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPre_CSMinus.ner[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSMinus.ner[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSPlus.ner[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSPlus.ner[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSMinus.ner[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$Nervous.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSMinus.ner[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$Nervous.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$AlonePre_CSPlus.ner[DBehav_Wide$Version_Alone=="V1"]   <-DBehav_Wide$Nervous.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSPlus.ner[DBehav_Wide$Version_Alone=="V2"]   <-DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePre_CSMinus.ner[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSMinus.ner[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSPlus.ner[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSPlus.ner[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSMinus.ner[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$Nervous.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSMinus.ner[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$Nervous.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Alone=="V2"]
```

create difference scores- substract CS- from CS+ for pre and post ratings
```{r}
#first, create a variable for each run order (v1 and v2)
#like question
#a more negative score means that the CS+ was less liked than the CSminus
  DBehav_Wide$v1_Pre_PlusMinMinus  <- DBehav_Wide$Like.RESP.v1_Pre_CSPlus - DBehav_Wide$Like.RESP.v1_Pre_CSMinus
  DBehav_Wide$v1_Post_PlusMinMinus <- DBehav_Wide$Like.RESP.v1_Post_CSPlus- DBehav_Wide$Like.RESP.v1_Post_CSMinus
  DBehav_Wide$v2_Pre_PlusMinMinus  <- DBehav_Wide$Like.RESP.v2_Pre_CSPlus - DBehav_Wide$Like.RESP.v2_Pre_CSMinus
  DBehav_Wide$v2_Post_PlusMinMinus <- DBehav_Wide$Like.RESP.v2_Post_CSPlus- DBehav_Wide$Like.RESP.v2_Post_CSMinus
  
#nervous question
#a more positive score means that the CS+ made participants more nervous than the CS-
  DBehav_Wide$v1_Pre_PlusMinMinus.ner  <- DBehav_Wide$Nervous.RESP.v1_Pre_CSPlus - DBehav_Wide$Nervous.RESP.v1_Pre_CSMinus
  DBehav_Wide$v1_Post_PlusMinMinus.ner <- DBehav_Wide$Nervous.RESP.v1_Post_CSPlus- DBehav_Wide$Nervous.RESP.v1_Post_CSMinus
  DBehav_Wide$v2_Pre_PlusMinMinus.ner  <- DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus - DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus
  DBehav_Wide$v2_Post_PlusMinMinus.ner <- DBehav_Wide$Nervous.RESP.v2_Post_CSPlus- DBehav_Wide$Nervous.RESP.v2_Post_CSMinus
  
#next, create difference score according to condition (parent vs. alone) 
  #Like question
  DBehav_Wide$Parent_Pre_PlusMinMinus <- NA
  DBehav_Wide$Alone_Pre_PlusMinMinus <- NA
  DBehav_Wide$Parent_Post_PlusMinMinus <- NA
  DBehav_Wide$Alone_Post_PlusMinMinus <- NA
  
  DBehav_Wide$Parent_Pre_PlusMinMinus[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$v1_Pre_PlusMinMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$Parent_Pre_PlusMinMinus[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$v2_Pre_PlusMinMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$Alone_Pre_PlusMinMinus[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$v1_Pre_PlusMinMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$Alone_Pre_PlusMinMinus[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$v2_Pre_PlusMinMinus[DBehav_Wide$Version_Alone=="V2"]
  
  DBehav_Wide$Parent_Post_PlusMinMinus[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$v1_Post_PlusMinMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$Parent_Post_PlusMinMinus[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$v2_Post_PlusMinMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$Alone_Post_PlusMinMinus[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$v1_Post_PlusMinMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$Alone_Post_PlusMinMinus[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$v2_Post_PlusMinMinus[DBehav_Wide$Version_Alone=="V2"]
  
  #Nervous question
  DBehav_Wide$Parent_Pre_PlusMinMinus.ner <- NA
  DBehav_Wide$Alone_Pre_PlusMinMinus.ner <- NA
  DBehav_Wide$Parent_Post_PlusMinMinus.ner <- NA
  DBehav_Wide$Alone_Post_PlusMinMinus.ner <- NA
  
  DBehav_Wide$Parent_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$v1_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$Parent_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$v2_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$Alone_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$v1_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$Alone_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$v2_Pre_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V2"]
  
  DBehav_Wide$Parent_Post_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$v1_Post_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$Parent_Post_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$v2_Post_PlusMinMinus.ner[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$Alone_Post_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$v1_Post_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$Alone_Post_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$v2_Post_PlusMinMinus.ner[DBehav_Wide$Version_Alone=="V2"]
  
```

look at the variables' descriptive statistics
```{r}
#like question
  describe(DBehav_Wide[,c("ParentPre_CSMinus","ParentPost_CSMinus","ParentPre_CSPlus","ParentPost_CSPlus",
                          "AlonePre_CSMinus","AlonePost_CSMinus","AlonePre_CSPlus","AlonePost_CSPlus")])

#nervous question
  describe (DBehav_Wide[,c("ParentPre_CSMinus.ner","ParentPost_CSMinus.ner","ParentPre_CSPlus.ner","ParentPost_CSPlus.ner",
                           "AlonePre_CSMinus.ner","AlonePost_CSMinus.ner","AlonePre_CSPlus.ner","AlonePost_CSPlus.ner")])

#difference score-like question
  describe(DBehav_Wide[,c("Parent_Pre_PlusMinMinus","Parent_Post_PlusMinMinus",
                          "Alone_Pre_PlusMinMinus","Alone_Post_PlusMinMinus")])
  
#difference score-nervous question
  describe(DBehav_Wide[,c("Parent_Pre_PlusMinMinus.ner","Parent_Post_PlusMinMinus.ner",
                          "Alone_Pre_PlusMinMinus.ner","Alone_Post_PlusMinMinus.ner")])

```

preliminary analyses- relation with age and sex
```{r}
#relation with sex
t.test (data = DBehav_Wide, Parent_Pre_PlusMinMinus ~ SEX)
t.test (data = DBehav_Wide, Parent_Post_PlusMinMinus ~ SEX)
t.test (data = DBehav_Wide, Alone_Pre_PlusMinMinus ~ SEX)
t.test (data = DBehav_Wide, Alone_Post_PlusMinMinus ~ SEX)

t.test (data = DBehav_Wide, Parent_Pre_PlusMinMinus.ner ~ SEX)
t.test (data = DBehav_Wide, Parent_Post_PlusMinMinus.ner ~ SEX)
t.test (data = DBehav_Wide, Alone_Pre_PlusMinMinus.ner ~ SEX)
t.test (data = DBehav_Wide, Alone_Post_PlusMinMinus.ner ~ SEX)

#relation with age
cor.test (DBehav_Wide$Parent_Pre_PlusMinMinus, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Parent_Post_PlusMinMinus, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Alone_Pre_PlusMinMinus, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Alone_Post_PlusMinMinus, DBehav_Wide$MRI_AGE )

cor.test (DBehav_Wide$Parent_Pre_PlusMinMinus.ner, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Parent_Post_PlusMinMinus.ner, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Alone_Pre_PlusMinMinus.ner, DBehav_Wide$MRI_AGE )
cor.test (DBehav_Wide$Alone_Post_PlusMinMinus.ner, DBehav_Wide$MRI_AGE )

```

create a long format for the difference scores
```{r}
 DBehav_Longdif <- DBehav_Wide[,c("Subject",
                                  "Parent_Pre_PlusMinMinus","Parent_Post_PlusMinMinus",
                                  "Alone_Pre_PlusMinMinus","Alone_Post_PlusMinMinus",
                                  "Parent_Pre_PlusMinMinus.ner","Parent_Post_PlusMinMinus.ner",
                                  "Alone_Pre_PlusMinMinus.ner","Alone_Post_PlusMinMinus.ner")]

#change vars names
 colnames(DBehav_Longdif) <- gsub("_PlusMinMinus","",colnames(DBehav_Longdif))
 colnames(DBehav_Longdif) <- gsub("_","",colnames(DBehav_Longdif))
 col <- colnames(DBehav_Longdif)
 colnames(DBehav_Longdif)[c(which(col=="ParentPre.ner"),which(col=="ParentPost.ner"),which(col=="AlonePre.ner"),which(col=="AlonePost.ner"))] <-
                          c("NervousRESP_ParentPre","NervousRESP_ParentPost","NervousRESP_AlonePre","NervousRESP_AlonePost")
 colnames(DBehav_Longdif)[c(which(col=="ParentPre"),which(col=="ParentPost"), which(col=="AlonePre"),which(col=="AlonePost"))] <-
                          c("LikeRESP_ParentPre","LikeRESP_ParentPost","LikeRESP_AlonePre","LikeRESP_AlonePost")
 
#turn to long format 
 DBehav_Longdif <- reshape(DBehav_Longdif,idvar="Subject", timevar = "versiontime",
                                varying=colnames(DBehav_Longdif)[2:9],direction="long", sep="_")
  
 DBehav_Longdif$version <-NA
 DBehav_Longdif$version[DBehav_Longdif$versiontime=="ParentPre"|DBehav_Longdif$versiontime=="ParentPost"] <- "Parent"
 DBehav_Longdif$version[DBehav_Longdif$versiontime=="AlonePre"|DBehav_Longdif$versiontime=="AlonePost"] <- "Alone"
  
 DBehav_Longdif$time <-NA
 DBehav_Longdif$time[DBehav_Longdif$versiontime=="ParentPre"| DBehav_Longdif$versiontime=="AlonePre"] <- "1Pre"
 DBehav_Longdif$time[DBehav_Longdif$versiontime=="ParentPost"| DBehav_Longdif$versiontime=="AlonePost"] <- "2Post"
 
#verify that means stay the same after reshaping
 describeBy(data=DBehav_Longdif, LikeRESP ~ time+version)  
 describeBy(data=DBehav_Longdif, NervousRESP ~ time+version)
#all good
  
```

statistical test- like question
```{r}

#two-way anova
  LikeRESP_anovatest <- anova_test(data = DBehav_Longdif, dv = LikeRESP, wid = Subject,within = c(version, time), type=3, effect.size = "pes")
  get_anova_table(LikeRESP_anovatest, correction ="GG")
  
#investigate simple effects - with ttests
  t.test (DBehav_Wide$Parent_Post_PlusMinMinus,DBehav_Wide$Parent_Pre_PlusMinMinus,paired = TRUE, alternative = "two.sided")
  t.test (DBehav_Wide$Alone_Post_PlusMinMinus, DBehav_Wide$Alone_Pre_PlusMinMinus,paired = TRUE, alternative = "two.sided")
  #using Benjamin Hochberg calculator (https://www.sdmproject.com/utilities/?show=FDR), adjusted pvalue for the parent simple effect is p = .052
  
#just for verification: investigate simple effects with anova
  LikeRESP_bycond <- DBehav_Longdif %>%
    group_by(version) %>%
    anova_test(dv = LikeRESP, wid = Subject, within = time) %>%
    get_anova_table() %>%
    adjust_pvalue(method = "hochberg") %>%
    ungroup
  
  LikeRESP_bycond
  
#visualization
#a) summarize overall group effects by condition
  sum_like_dif_se <- summarySE(data = DBehav_Longdif, measurevar="LikeRESP", groupvars =c("version","time"),
             na.rm = T, conf.interval = 0.95,.drop = TRUE)
  
#b) plot
  LikeRESP_plot <- ggplot(data = as.data.frame(sum_like_dif_se), aes(x = time, y = LikeRESP, group=version, colour = version)) + 
    geom_path(alpha = 0.2, size = 0.2) +
    geom_errorbar(aes(ymin=LikeRESP-se, ymax=LikeRESP+se), width=.1, position=position_dodge(0.05)) +
    geom_line(aes(x = time, y = LikeRESP,color = version), size = 2.5) +
    labs (x = "time", y = "Like rating difference (CS+ > CS-) ") +
    scale_x_discrete(labels=c("Pre-learning", "Post-learning")) +
    ylim(-1, 1) +
    theme_classic() +
    scale_color_brewer(palette="Set2") +
    scale_linetype_manual(values=c("dashed", "solid")) +
    theme(axis.text = element_text(size = 16) , axis.title = element_text(size = 20))
  LikeRESP_plot
   
```

statistical test- nervous question
```{r}

#two-way anova
  NervousRESP_anovatest <- anova_test(data = DBehav_Longdif, dv = NervousRESP, wid = Subject,within = c(version, time), type=3, effect.size = "pes")
  get_anova_table(NervousRESP_anovatest, correction = "GG")
  
#investigate the main effect of time 
  DBehav_Wide$Bothcond_Post_PlusMinMinus.ner <- rowMeans(DBehav_Wide[,c("Parent_Post_PlusMinMinus.ner","Alone_Post_PlusMinMinus.ner")],na.rm=T)
  DBehav_Wide$Bothcond_Pre_PlusMinMinus.ner <- rowMeans(DBehav_Wide[,c("Parent_Pre_PlusMinMinus.ner","Alone_Pre_PlusMinMinus.ner")],na.rm=T)
  
  describe(DBehav_Wide[,c("Bothcond_Post_PlusMinMinus.ner","Bothcond_Pre_PlusMinMinus.ner")])
#descriptive statistics without subject 56 (has no nervous data in the parent condition)
  describe(DBehav_Wide[DBehav_Wide$Subject!=56,c("Bothcond_Post_PlusMinMinus.ner","Bothcond_Pre_PlusMinMinus.ner")])
  t.test (DBehav_Wide$Bothcond_Post_PlusMinMinus.ner,DBehav_Wide$Bothcond_Pre_PlusMinMinus.ner,paired = TRUE, alternative = "two.sided")
#t.test without subject 56 for the same reason
  t.test (DBehav_Wide$Bothcond_Post_PlusMinMinus.ner[DBehav_Wide$Subject!=56],
          DBehav_Wide$Bothcond_Pre_PlusMinMinus.ner[DBehav_Wide$Subject!=56],
          paired = TRUE, alternative = "two.sided")
  
  
#visualization
#a) summarize overall group effects by condition
  sum_nervous_dif_se <- summarySE(data = DBehav_Longdif, measurevar="NervousRESP", groupvars =c("version","time"),
             na.rm = T, conf.interval = 0.95,.drop = TRUE)
  
#b) plot
  NervousRESP_plot <- ggplot(data = as.data.frame(sum_nervous_dif_se), aes(x = time, y = NervousRESP, group=version, colour = version)) + 
    geom_path(alpha = 0.2, size = 0.2) +
    geom_errorbar(aes(ymin=NervousRESP-se, ymax=NervousRESP+se), width=.1, position=position_dodge(0.05)) +
    geom_line(aes(x = time, y = NervousRESP,color = version), size = 2.5) +
    labs (x = "time", y = "Nervousness rating difference (CS+ > CS-) ") +
    scale_x_discrete(labels=c("Pre-learning", "Post-learning")) +
    ylim(-1, 1) +
    theme_classic() +
    scale_color_brewer(palette="Set2") +
    scale_linetype_manual(values=c("dashed", "solid")) +
    theme(axis.text = element_text(size = 16) , axis.title = element_text(size = 20))
  NervousRESP_plot
```
checking both nervous and like question in the same analysis
```{r}
#turn to an even longer format 
  DBehav_Longdif_Like <- DBehav_Longdif
  DBehav_Longdif_Like$RESP <- DBehav_Longdif_Like$LikeRESP
  DBehav_Longdif_Like$question <- "like"
  #change the direction of the like rating to be consistent with the nervous rating. Here a more positive score means that the CS+ was LESS liked than the CS-
  DBehav_Longdif_Like$RESP <- DBehav_Longdif_Like$RESP *-1
  
  DBehav_Longdif_Nervous <- DBehav_Longdif
  DBehav_Longdif_Nervous$RESP <- DBehav_Longdif_Nervous$NervousRESP
  DBehav_Longdif_Nervous$question <- "nervous"
  
  DBehav_Longerdif <- rbind(DBehav_Longdif_Like,DBehav_Longdif_Nervous)
  col <- colnames(DBehav_Longerdif)
  DBehav_Longerdif <- DBehav_Longerdif[,-c(which (col=="LikeRESP"),which(col=="NervousRESP"))]
  
#anova
  RESP_anovatest <- anova_test(data = DBehav_Longerdif, dv = RESP, wid = Subject, within = c(question, version, time), 
                               type=3, effect.size = "pes")
  get_anova_table(RESP_anovatest, correction = "GG")
  
#check that I get the same results with formula syntax
  RESP_anovatest <- anova_test(data = DBehav_Longerdif, RESP ~ question*version*time + Error(Subject/(question*version*time)), 
                               type=3,effect.size = "pes")
  get_anova_table(RESP_anovatest, correction = "GG")
  
#check that I get the same results with aov function
  RESP_aov <- aov(data=DBehav_Longerdif, RESP ~ question*version*time+ Error(factor(Subject)/(question*version*time)))
  summary(RESP_aov)
  #not exactly the same but similar. Something is specified wrong here because the model is singular. In any events, the question*time interaction
  #is significant also here and many of the effects turn the same. So I count the anova_test function and continue with it. 
  

#check the two-way interaction
RESP_qxt_anovatest <- DBehav_Longerdif %>% 
  group_by(version) %>%
  anova_test(dv = RESP, wid = Subject,within = c(question,time), type=3, effect.size = "pes") 
get_anova_table(RESP_qxt_anovatest, correction = "GG")

RESP_bothcond <- aggregate(DBehav_Longerdif$RESP,by=list(DBehav_Longerdif$Subject,DBehav_Longerdif$time,DBehav_Longerdif$question), FUN="mean")
colnames(RESP_bothcond) <- c("Subject","time","question","RESP")

RESP_bothcond_anovatest <- RESP_bothcond %>% 
  group_by(question) %>%
  anova_test(dv = RESP, wid = Subject,within = c(time), type=3, effect.size = "pes") 
get_anova_table(RESP_bothcond_anovatest, correction = "GG")


#look at descriptives
describeBy(data=RESP_bothcond[RESP_bothcond$question=="like",], RESP~time) 
describeBy(data=RESP_bothcond[RESP_bothcond$question=="nervous",], RESP~time) 

RESP_bothcond_simpletest <- RESP_bothcond %>%
    group_by(question) %>%
    anova_test(dv = RESP, wid = Subject, within = time) %>%
    get_anova_table() %>%
    adjust_pvalue(method = "hochberg") %>%
    ungroup
RESP_bothcond_simpletest

#investigate with ttests
RESP_bothcond_Wide <- RESP_bothcond
RESP_bothcond_Wide$ques_time <- paste0(RESP_bothcond_Wide$question,RESP_bothcond_Wide$time)
RESP_bothcond_Wide <- reshape(RESP_bothcond_Wide, timevar="ques_time",idvar="Subject", direction="wide")

describe(RESP_bothcond_Wide[,c("RESP.like1Pre","RESP.like2Post")])
t.test (RESP_bothcond_Wide$RESP.like2Post,RESP_bothcond_Wide$RESP.like1Pre,paired = TRUE, alternative = "two.sided")
  
describe(RESP_bothcond_Wide[,c("RESP.nervous1Pre","RESP.nervous2Post")])
t.test (RESP_bothcond_Wide$RESP.nervous2Post,RESP_bothcond_Wide$RESP.nervous1Pre,paired = TRUE, alternative = "two.sided")
#using BHC calculator, adjusted p is 0.0010972

#hlm
  RESP_hlm <- lmer(data=DBehav_Longerdif, RESP ~ question*version*time+ (1|Subject))
  summary(RESP_hlm)
  
```

