---
title: "parental_effects_on_fear_learning_analyses"
author: "Lior Abramson"
date: "November 2023"
output: html_document
---

1:: preparations
#house keeping:
```{r setup, include=FALSE}
  rm(list = ls())
  cat ("\014")
  if(is.null(dev.list()) == FALSE) dev.off()

#Packages
  packages <- c('reshape','psych','tidyverse','Rmisc','lme4','ggplot2','report')
  lapply(packages, require, character.only = TRUE)
```

#load behavioral data:
```{r}
#load data
  D <- read.csv("data/classical_conditioning_behavior_data.csv")
```

#organize data:
```{r}
#create a data with only like+nervous rating rows
  DBehav <- D[!is.na(D$LikePre.RESP)|!is.na(D$LikePost.RESP),] 
  
#put the pre and post ratings under the same variable
  DBehav$Like.RESP <- NA
  DBehav$Like.RESP[!is.na(DBehav$LikePre.RESP)]  <- DBehav$LikePre.RESP[!is.na(DBehav$LikePre.RESP)] 
  DBehav$Like.RESP[!is.na(DBehav$LikePost.RESP)] <- DBehav$LikePost.RESP[!is.na(DBehav$LikePost.RESP)]
  
  DBehav$Nervous.RESP <- NA
  DBehav$Nervous.RESP[!is.na(DBehav$NervousPre.RESP)]  <- DBehav$NervousPre.RESP[!is.na(DBehav$NervousPre.RESP)] 
  DBehav$Nervous.RESP[!is.na(DBehav$NervousPost.RESP)] <- DBehav$NervousPost.RESP[!is.na(DBehav$NervousPost.RESP)]

#create a variable indicating the time (pre/post conditioning)
  DBehav$time <- NA
  DBehav$time[!is.na(DBehav$LikePre.RESP)]  <-"Pre"
  DBehav$time[!is.na(DBehav$LikePost.RESP)] <-"Post"
  
#create a variable indicating the time, the version (which fractals the subject watched) and the stimulus (CS+/CS-)
  DBehav$version_time_and_stim <- paste0(DBehav$Version,"_",DBehav$time,"_",DBehav$Shape)
  
#take only relevant variables 
  DBehav <- DBehav[,c("Subject","Like.RESP","Nervous.RESP","version_time_and_stim")]
  
```

#add information about parental presence (present/absence)
```{r}
#turn to wide format
#ignore warning message (it refers to a subject who is about to be removed from the file anyway)
  DBehav_Wide <- reshape(DBehav, timevar="version_time_and_stim",idvar="Subject", direction="wide")

#import condition data
  DParentInfo <- read.csv("data/classical_conditioning_parental_presence_data.csv")
  DBehav_Wide <- merge(DBehav_Wide,DParentInfo[,c("Subject","Version_Parent","Version_Alone","First_Cond")], by="Subject", all.x=T, all.y=F)
```

#create a long format of parental context information to attach to fMRI data
```{r}
  DParentInfoLong <- DParentInfo[,c("Subject","Scan_Parent","Scan_Alone")]
  DParentInfoLong <- reshape(DParentInfoLong, idvar="Subject", timevar="Parent_Alone", 
                               varying=colnames(DParentInfoLong)[2:3],direction="long",sep="_")
  colnames(DParentInfoLong)[colnames(DParentInfoLong)=="Scan"] <- "order"
```

#add demographic details
#NOTE: this data is not shared online due to privacy considerations and IRB constraints
```{r}
#import data
  DDemographics <- read.csv("../data/subjects_demographics.csv")

#manually change MRI_age according to Tristan's corrections
  DDemographics$MRI_AGE_orig <- DDemographics$MRI_AGE #keep original
  DDemographics$MRI_AGE[DDemographics$Subject_real_id==45] <- 11.21
  DDemographics$MRI_AGE[DDemographics$Subject_real_id==4] <- 14.34
  DDemographics$MRI_AGE[DDemographics$Subject_real_id==5] <- 17.61
  DDemographics$MRI_AGE[DDemographics$Subject_real_id==32] <- 8.11
  DDemographics$MRI_AGE[DDemographics$Subject_real_id==44] <- 9.20
  
  
  DBehav_Wide <- merge(DBehav_Wide,DDemographics[,c("Subject","SEX","MRI_AGE","DEM_4_RACE_CHILD","DEM_4_RACE_CHILD_OTHER","AIOI_P1_EDU","AIOI_P2_EDU","AIOI_P1_Income","AIOI_P2_Income")], by="Subject", all.x=T, all.y=F)
  

  
#check age, sex and race of the sample
  #age
  describe(DBehav_Wide$MRI_AGE)
  #sex
  summary(as.factor(DBehav_Wide$SEX))
  #race
  summary(as.factor(DBehav_Wide$DEM_4_RACE_CHILD))
  
#check education-code education to a binary variable of less/more than a BA degree
  DBehav_Wide <- DBehav_Wide%>%
    mutate(edu_p1_binary = ifelse(AIOI_P1_EDU < 5,"<BA","BA>"),
           edu_p2_binary = ifelse(AIOI_P2_EDU < 5,"<BA","BA>"),
           edu_atleast1_BA = ifelse(edu_p1_binary=="BA>"|edu_p2_binary=="BA>","yes","no"))
  summary(as.factor(DBehav_Wide$edu_atleast1_BA))
  
  #income
  summary(as.factor(DBehav_Wide$AIOI_P1_Income))
  summary(as.factor(DBehav_Wide$AIOI_P2_Income))
  
  #recode the likert scale income to reflect minimum (i.e., the parent makes at least this sum or more)
  DBehav_Wide$AIOI_P1_Income_min <- 
    as.numeric(recode(
    DBehav_Wide$AIOI_P1_Income,
    `1` = "0",
    `2` = "10001",
    `3` = "25001",
    `4` = "40001",
    `5` = "55001",
    `6` = "70001",
    `7` = "85001",
    `8` = "100001",
    `9` = "150001",
    `10` = "200001",
  ))
  
  
  DBehav_Wide$AIOI_P2_Income_min <- 
    as.numeric(recode(
    DBehav_Wide$AIOI_P2_Income,
    `1` = "0",
    `2` = "10001",
    `3` = "25001",
    `4` = "40001",
    `5` = "55001",
    `6` = "70001",
    `7` = "85001",
    `8` = "100001",
    `9` = "150001",
    `10` = "200001",
  ))
  
 DBehav_Wide$income_min_household <- DBehav_Wide$AIOI_P1_Income_min+DBehav_Wide$AIOI_P2_Income_min
 
 #how many make more than 75,157$ as a household (more than the median in New York for 2017-2021: https://www.census.gov/quickfacts/fact/table/NY,newyorkcountynewyork/INC110221)
 DBehav_Wide <- DBehav_Wide%>%
   mutate(min_income_bin_median = ifelse(income_min_household>75157,1,0))
 
 summary(as.factor(DBehav_Wide$min_income_bin_median))
   
```

#exclude participants (from both long and wide dataframes) and check demographic characteristics of final sample
```{r}
#remove subjects 289 and 299 (experimenter error- watched the same shapes in both parental presence and absence conditions)
#remove subjects 158 and 323 (did not complete both conditions)
  DBehav <- DBehav[DBehav$Subject!=289 & DBehav$Subject!=299 & DBehav$Subject!=158 & DBehav$Subject!=323,]
  DBehav_Wide <- DBehav_Wide[DBehav_Wide$Subject!=289 & DBehav_Wide$Subject!=299 & DBehav_Wide$Subject!=158 & DBehav_Wide$Subject!=323,]
  
#remove nervous rating data of subject 239 from v2- the parental absence condition (was not asked this question in the parent presence condition due to experimenter error)
DBehav$Nervous.RESP[DBehav$Subject==239] <- NA
DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus[DBehav_Wide$Subject==239] <- NA
DBehav_Wide$Nervous.RESP.v2_Post_CSPlus[DBehav_Wide$Subject==239] <- NA
DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus[DBehav_Wide$Subject==239] <- NA
DBehav_Wide$Nervous.RESP.v2_Post_CSMinus[DBehav_Wide$Subject==239] <- NA

#check age, sex and race for the final behavioral sample
  #age
  describe(DBehav_Wide$MRI_AGE)
  #sex
  summary(as.factor(DBehav_Wide$SEX))
```

#create raw rating scores for each parental presence condition in the wide format
```{r}
#like question
  #initialize variables
  DBehav_Wide$ParentPre_CSPlus <- NA
  DBehav_Wide$ParentPre_CSMinus <- NA
  DBehav_Wide$AlonePre_CSPlus <- NA
  DBehav_Wide$AlonePre_CSMinus <- NA
  
  DBehav_Wide$ParentPost_CSPlus <- NA
  DBehav_Wide$ParentPost_CSMinus <- NA
  DBehav_Wide$AlonePost_CSPlus <- NA
  DBehav_Wide$AlonePost_CSMinus <- NA
  
  DBehav_Wide$ParentPre_CSPlus[DBehav_Wide$Version_Parent=="V1"]   <-DBehav_Wide$Like.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSPlus[DBehav_Wide$Version_Parent=="V2"]   <-DBehav_Wide$Like.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPre_CSMinus[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Like.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSMinus[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Like.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSPlus[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Like.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSPlus[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Like.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSMinus[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$Like.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSMinus[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$Like.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$AlonePre_CSPlus[DBehav_Wide$Version_Alone=="V1"]   <-DBehav_Wide$Like.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSPlus[DBehav_Wide$Version_Alone=="V2"]   <-DBehav_Wide$Like.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePre_CSMinus[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Like.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSMinus[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Like.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSPlus[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Like.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSPlus[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Like.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSMinus[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$Like.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSMinus[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$Like.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Alone=="V2"] 
  
#nervous question
  #initialize variables
  DBehav_Wide$ParentPre_CSPlus.ner <- NA
  DBehav_Wide$ParentPre_CSMinus.ner <- NA
  DBehav_Wide$AlonePre_CSPlus.ner <- NA
  DBehav_Wide$AlonePre_CSMinus.ner <- NA
  
  DBehav_Wide$ParentPost_CSPlus.ner <- NA
  DBehav_Wide$ParentPost_CSMinus.ner <- NA
  DBehav_Wide$AlonePost_CSPlus.ner <- NA
  DBehav_Wide$AlonePost_CSMinus.ner <- NA
  
  DBehav_Wide$ParentPre_CSPlus.ner[DBehav_Wide$Version_Parent=="V1"]   <-DBehav_Wide$Nervous.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSPlus.ner[DBehav_Wide$Version_Parent=="V2"]   <-DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPre_CSMinus.ner[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPre_CSMinus.ner[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSPlus.ner[DBehav_Wide$Version_Parent=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSPlus.ner[DBehav_Wide$Version_Parent=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Parent=="V2"]
  DBehav_Wide$ParentPost_CSMinus.ner[DBehav_Wide$Version_Parent=="V1"] <-DBehav_Wide$Nervous.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Parent=="V1"]
  DBehav_Wide$ParentPost_CSMinus.ner[DBehav_Wide$Version_Parent=="V2"] <-DBehav_Wide$Nervous.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Parent=="V2"]
  
  DBehav_Wide$AlonePre_CSPlus.ner[DBehav_Wide$Version_Alone=="V1"]   <-DBehav_Wide$Nervous.RESP.v1_Pre_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSPlus.ner[DBehav_Wide$Version_Alone=="V2"]   <-DBehav_Wide$Nervous.RESP.v2_Pre_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePre_CSMinus.ner[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Pre_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePre_CSMinus.ner[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Pre_CSMinus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSPlus.ner[DBehav_Wide$Version_Alone=="V1"]  <-DBehav_Wide$Nervous.RESP.v1_Post_CSPlus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSPlus.ner[DBehav_Wide$Version_Alone=="V2"]  <-DBehav_Wide$Nervous.RESP.v2_Post_CSPlus[DBehav_Wide$Version_Alone=="V2"]
  DBehav_Wide$AlonePost_CSMinus.ner[DBehav_Wide$Version_Alone=="V1"] <-DBehav_Wide$Nervous.RESP.v1_Post_CSMinus[DBehav_Wide$Version_Alone=="V1"]
  DBehav_Wide$AlonePost_CSMinus.ner[DBehav_Wide$Version_Alone=="V2"] <-DBehav_Wide$Nervous.RESP.v2_Post_CSMinus[DBehav_Wide$Version_Alone=="V2"]
```

#create difference scores- substract CS- from CS+ for pre and post ratings
```{r}
#like question
  DBehav_Wide$Parent_Pre_PlusMinMinus <- DBehav_Wide$ParentPre_CSPlus- DBehav_Wide$ParentPre_CSMinus
  DBehav_Wide$Alone_Pre_PlusMinMinus <- DBehav_Wide$AlonePre_CSPlus- DBehav_Wide$AlonePre_CSMinus
  DBehav_Wide$Parent_Post_PlusMinMinus <- DBehav_Wide$ParentPost_CSPlus- DBehav_Wide$ParentPost_CSMinus
  DBehav_Wide$Alone_Post_PlusMinMinus <- DBehav_Wide$AlonePost_CSPlus- DBehav_Wide$AlonePost_CSMinus
  
#nervous question
  DBehav_Wide$Parent_Pre_PlusMinMinus.ner <- DBehav_Wide$ParentPre_CSPlus.ner- DBehav_Wide$ParentPre_CSMinus.ner
  DBehav_Wide$Alone_Pre_PlusMinMinus.ner <- DBehav_Wide$AlonePre_CSPlus.ner- DBehav_Wide$AlonePre_CSMinus.ner
  DBehav_Wide$Parent_Post_PlusMinMinus.ner <- DBehav_Wide$ParentPost_CSPlus.ner- DBehav_Wide$ParentPost_CSMinus.ner
  DBehav_Wide$Alone_Post_PlusMinMinus.ner <- DBehav_Wide$AlonePost_CSPlus.ner- DBehav_Wide$AlonePost_CSMinus.ner
```

#look at the variables' descriptive statistics
```{r}
#like question
  describe(DBehav_Wide[,c("ParentPre_CSMinus","ParentPost_CSMinus","ParentPre_CSPlus","ParentPost_CSPlus",
                          "AlonePre_CSMinus","AlonePost_CSMinus","AlonePre_CSPlus","AlonePost_CSPlus")])

#nervous question
  describe (DBehav_Wide[,c("ParentPre_CSMinus.ner","ParentPost_CSMinus.ner","ParentPre_CSPlus.ner","ParentPost_CSPlus.ner",
                           "AlonePre_CSMinus.ner","AlonePost_CSMinus.ner","AlonePre_CSPlus.ner","AlonePost_CSPlus.ner")])

#difference score-like question
  describe(DBehav_Wide[,c("Parent_Pre_PlusMinMinus","Parent_Post_PlusMinMinus",
                          "Alone_Pre_PlusMinMinus","Alone_Post_PlusMinMinus")])
  
#difference score-nervous question
  describe(DBehav_Wide[,c("Parent_Pre_PlusMinMinus.ner","Parent_Post_PlusMinMinus.ner",
                          "Alone_Pre_PlusMinMinus.ner","Alone_Post_PlusMinMinus.ner")])

```

#create a long format for the difference scores and add sex and age information
```{r}
 DBehav_Longdif <- DBehav_Wide[,c("Subject",
                                  "Parent_Pre_PlusMinMinus","Parent_Post_PlusMinMinus",
                                  "Alone_Pre_PlusMinMinus","Alone_Post_PlusMinMinus",
                                  "Parent_Pre_PlusMinMinus.ner","Parent_Post_PlusMinMinus.ner",
                                  "Alone_Pre_PlusMinMinus.ner","Alone_Post_PlusMinMinus.ner")]

#change vars names
 colnames(DBehav_Longdif) <- gsub("_PlusMinMinus","",colnames(DBehav_Longdif))
 colnames(DBehav_Longdif) <- gsub("_","",colnames(DBehav_Longdif))
 col <- colnames(DBehav_Longdif)
 colnames(DBehav_Longdif)[c(which(col=="ParentPre.ner"),which(col=="ParentPost.ner"),which(col=="AlonePre.ner"),which(col=="AlonePost.ner"))] <-
                          c("NervousRESP_ParentPre","NervousRESP_ParentPost","NervousRESP_AlonePre","NervousRESP_AlonePost")
 colnames(DBehav_Longdif)[c(which(col=="ParentPre"),which(col=="ParentPost"), which(col=="AlonePre"),which(col=="AlonePost"))] <-
                          c("LikeRESP_ParentPre","LikeRESP_ParentPost","LikeRESP_AlonePre","LikeRESP_AlonePost")
 
#turn to long format 
 DBehav_Longdif <- reshape(DBehav_Longdif,idvar="Subject", timevar = "versiontime",
                                varying=colnames(DBehav_Longdif)[2:9],direction="long", sep="_")
  
#create parental presence condition and time variables
 DBehav_Longdif$version <-NA
 DBehav_Longdif$version[DBehav_Longdif$versiontime=="ParentPre"|DBehav_Longdif$versiontime=="ParentPost"] <- "Parent"
 DBehav_Longdif$version[DBehav_Longdif$versiontime=="AlonePre"|DBehav_Longdif$versiontime=="AlonePost"] <- "Alone"
  
 DBehav_Longdif$time <-NA
 DBehav_Longdif$time[DBehav_Longdif$versiontime=="ParentPre"| DBehav_Longdif$versiontime=="AlonePre"] <- "1Pre"
 DBehav_Longdif$time[DBehav_Longdif$versiontime=="ParentPost"| DBehav_Longdif$versiontime=="AlonePost"] <- "2Post"
 
#verify that means and sd stay the same after reshaping
 describeBy(data=DBehav_Longdif, LikeRESP ~ time+version)  
 describeBy(data=DBehav_Longdif, NervousRESP ~ time+version)
#all good
  
#add sex and age information
 DBehav_Longdif <- merge(DBehav_Longdif,DBehav_Wide[,c("Subject","SEX","MRI_AGE")],
                              by="Subject", all.x=T, all.y=F)
 
 #add order information
 #temporarily switch variable name
 colnames(DParentInfoLong)[which(colnames(DParentInfoLong)=="Parent_Alone")] <- "version"
 DBehav_Longdif <- merge(DBehav_Longdif,DParentInfoLong, by=c("Subject","version"), all.x=T, all.y=F)
 #switch back the variable name for later merging
 colnames(DParentInfoLong)[which(colnames(DParentInfoLong)=="version")] <- "Parent_Alone"

```


2:: Behavioral analyses
#statistical test- like question
```{r}
#code independent variables: create effect coding for binary variables and mean-center continuous variables
  DBehav_Longdif <- DBehav_Longdif %>%
    dplyr::mutate(SEX_num = ifelse(SEX=="m",-1,1),
                  version_num = ifelse(version=="Alone",-1,1),
                  time_num = ifelse(time=="1Pre",-1,1),
                  order_num = ifelse(order=="cond1",-1,1),
                  MRI_AGE_c = scale(MRI_AGE, scale=F))
   
#multilevel linear regression controlling for age, sex, and order
  model_like_control_sex_age_order <-lmer(data= DBehav_Longdif, 
                                    LikeRESP~ version_num*time_num + SEX_num + MRI_AGE_c + order_num+ (1|Subject))
  report(model_like_control_sex_age_order)

#visualization
  #a) summarize overall group effects by condition
#  sum_like_dif_se <- summarySE(data = DBehav_Longdif, measurevar="LikeRESP", groupvars =c("version","time"),
#             na.rm = T, conf.interval = 0.95,.drop = TRUE)
  
  #b) plot
#  LikeRESP_plot <- ggplot(data = as.data.frame(sum_like_dif_se), aes(x = time, y = LikeRESP, group=version, colour = version)) + 
#    geom_path(alpha = 0.2, size = 0.2) +
#    geom_errorbar(aes(ymin=LikeRESP-se, ymax=LikeRESP+se), width=.1, position=position_dodge(0.05)) +
#    geom_line(aes(x = time, y = LikeRESP,color = version), size = 2.5) +
#    labs (x = "time", y = "Like rating difference (CS+ > CS-) ") +
#    scale_x_discrete(labels=c("Pre-conditioning", "Post-conditioning")) +
#    ylim(-1, 1) +
#    theme_classic() +
#    scale_color_brewer(palette="Set2", labels = c("Absence", "Presence")) +
#    scale_linetype_manual(values=c("dashed", "solid")) +
#    theme(axis.text = element_text(size = 25) , axis.title = element_text(size = 25))
#  LikeRESP_plot
  
```

#statistical test- nervous question
```{r}
#multilevel linear regression controlling for age, sex, and order 
  model_nervous_control_sex_age_order <-lmer(data= DBehav_Longdif, 
                                       NervousRESP~ version_num*time_num + SEX_num +MRI_AGE_c+ order_num + (1|Subject))
  report(model_nervous_control_sex_age_order)

#find means for time regardless of parental context condition (to better understand the main effect)
#a) summarize overall group effects by condition
#  sum_nervous_dif_se_both_parentcontextconds <- summarySE(data = DBehav_Longdif, measurevar="NervousRESP", groupvars =c("time"),
#             na.rm = T, conf.interval = 0.95,.drop = TRUE)

#visualization
  #a) summarize overall group effects by condition
#  sum_nervous_dif_se <- summarySE(data = DBehav_Longdif, measurevar="NervousRESP", groupvars =c("version","time"),
#             na.rm = T, conf.interval = 0.95,.drop = TRUE)
  
  #b) plot
#  NervousRESP_plot <- ggplot(data = as.data.frame(sum_nervous_dif_se), aes(x = time, y = NervousRESP, group=version, colour = version)) + 
#    geom_path(alpha = 0.2, size = 0.2) +
#    geom_errorbar(aes(ymin=NervousRESP-se, ymax=NervousRESP+se), width=.1, position=position_dodge(0.05)) +
#    geom_line(aes(x = time, y = NervousRESP,color = version), size = 2.5) +
#    labs (x = "Time", y = "Nervousness rating difference (CS+ > CS-) ") +
#    scale_x_discrete(labels=c("Pre-conditioning", "Post-conditioning")) +
#    ylim(-1, 1) +
#    theme_classic() +
#    scale_color_brewer(palette="Set2", labels = c("Absence", "Presence")) +
#    scale_linetype_manual(values=c("dashed", "solid")) +
#    theme(axis.text = element_text(size = 25) , axis.title = element_text(size = 25))
#  NervousRESP_plot
```


3:: Neural results
#organize file-mPFC data
```{r}
#condition 1
  DROI_mPFC_cond1 <- read.csv ("data/ROI_talairach_BA102432_-10-20_resample_NL6Asym_cond1.csv")
  valid_subj <- read.csv ("data/valid_fmri_participant_list.csv")
  DROI_mPFC_cond1$Subject <- rep(valid_subj$Subject, each=2)
  DROI_mPFC_cond1$Subject <- as.numeric(gsub("sub-","",DROI_mPFC_cond1$Subject))
  DROI_mPFC_cond1$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_mPFC_cond1 <- reshape(DROI_mPFC_cond1, timevar="contrast",idvar="Subject", direction="wide")
  DROI_mPFC_cond1$order <- "cond1"

#condition 2
  DROI_mPFC_cond2 <- read.csv ("data/ROI_talairach_BA102432_-10-20_resample_NL6Asym_cond2.csv")
  DROI_mPFC_cond2$Subject <- rep(valid_subj$Subject, each=2)
  DROI_mPFC_cond2$Subject <- as.numeric(gsub("sub-","",DROI_mPFC_cond2$Subject))
  DROI_mPFC_cond2$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_mPFC_cond2 <- reshape(DROI_mPFC_cond2, timevar="contrast",idvar="Subject", direction="wide")
  DROI_mPFC_cond2$order <- "cond2"

#combine conditions
  DROI_mPFC <- rbind(DROI_mPFC_cond1,DROI_mPFC_cond2)

#get parental context information
  DROI_mPFC <- merge(DROI_mPFC,DParentInfoLong, by=c("Subject","order"), all.x=T, all.y=F)

#merge with sex and age
  DROI_mPFC <- merge(DROI_mPFC,DBehav_Wide[,c("Subject","SEX","MRI_AGE")],
                              by="Subject", all.x=T, all.y=F)
 
#do effect coding for categorical variables and center continuous variables
  DROI_mPFC <- DROI_mPFC %>%
    dplyr::mutate(SEX_effectc = ifelse(SEX=="m",-1,1),
                  Parent_Alone_effectc = ifelse(Parent_Alone=="Alone",-1,1),
                  MRI_AGE_c = scale(MRI_AGE, scale=F),
                  order_effectc = ifelse(order=="cond1",-1,1))
  
#create a wide format for later plotting and visualization purposes 
  DROI_mPFC_wide <- reshape(DROI_mPFC, timevar="Parent_Alone",idvar="Subject", direction="wide")
```

#report age and sex for final fMRI sample
```{r}
#age
  describe(DROI_mPFC$MRI_AGE[DROI_mPFC$Parent_Alone=="Parent"]) #choose only one row per subject (doesn't matter which)
#sex
  summary(as.factor(DROI_mPFC$SEX[DROI_mPFC$Parent_Alone=="Parent"]))
```

#test results- mPFC: US vs. baseline contrast
```{r, include=F}
#look at the descriptive statistics
  describeBy (data= DROI_mPFC, mPFC_activation.noise_baseline~Parent_Alone)

#multilevel linear regression controlling for sex, age, and order
  lmer_mPFC_noise_baseline_sex_age_order <- lmer(data=DROI_mPFC, 
                                                 mPFC_activation.noise_baseline~ Parent_Alone_effectc*SEX_effectc + Parent_Alone_effectc*MRI_AGE_c + Parent_Alone_effectc*order_effectc + (1|Subject))
  report(lmer_mPFC_noise_baseline_sex_age_order)
  
#multilevel linear regression with no covariates
  lmer_mPFC_noise_baseline <- lmer(data=DROI_mPFC, mPFC_activation.noise_baseline~ Parent_Alone_effectc + (1|Subject))
  report(lmer_mPFC_noise_baseline)
```

#test results- mPFC: CS+ vs. CS- contrast
```{r}
#look at the descriptive statistics
  describeBy (data= DROI_mPFC, mPFC_activation.plus_minus~Parent_Alone)

#multilevel linear regression controlling for sex, age, and order
  lmer_mPFC_plus_minus_sex_age_order <- lmer(data=DROI_mPFC, 
                                             mPFC_activation.plus_minus~ 
                                             Parent_Alone_effectc*SEX_effectc + Parent_Alone_effectc*MRI_AGE_c + Parent_Alone_effectc*order_effectc + (1|Subject))
  report( lmer_mPFC_plus_minus_sex_age_order)
  
#multilevel linear regression with no covariates
  lmer_mPFC_plus_minus <- lmer(data=DROI_mPFC, mPFC_activation.plus_minus~ Parent_Alone_effectc + (1|Subject))
  report(lmer_mPFC_plus_minus)
  

#see how many subjects show decrease and how many show increase according to parental context
  DROI_mPFC_wide <- DROI_mPFC_wide %>%
  mutate(trend_mPFC_plusmin = ifelse(mPFC_activation.plus_minus.Parent>mPFC_activation.plus_minus.Alone,1,
                        ifelse(mPFC_activation.plus_minus.Parent<mPFC_activation.plus_minus.Alone,-1,NA))
         )

  DROI_mPFC <- merge(DROI_mPFC,DROI_mPFC_wide[,c("Subject","trend_mPFC_plusmin")],
                              by="Subject", all.x=T, all.y=F)
  
  summary(as.factor(DROI_mPFC_wide$trend_mPFC_plusmin))

#visualize results - separate colors for participants that showed increase or decrease in parental presence vs absence
  plot_mPFC_plusmin <- ggplot(data = DROI_mPFC, 
                                 aes(group=interaction(Subject,trend_mPFC_plusmin), x=Parent_Alone,y = mPFC_activation.plus_minus, color=as.factor(trend_mPFC_plusmin)))+
    geom_line(aes(group=interaction(Subject,trend_mPFC_plusmin), x=Parent_Alone,y=mPFC_activation.plus_minus, color=as.factor(trend_mPFC_plusmin)), size=1)+
     stat_summary(fun=mean,geom="line",lwd=2,color="black",aes(group=1))+
    scale_color_brewer(palette="Set2")+
    theme_classic() +
    labs (x = "", y = "Activation (CS+ vs. CS-)", title="")+
    theme(axis.text = element_text(size = 40) , axis.title = element_text(size = 40))+
    theme(legend.position="none", plot.title = element_text(hjust = 0.5, size=50))+
    scale_x_discrete(expand = expansion(mult=c(0.4,2)), labels=c("Absence", "Presence"))+
    scale_y_continuous(limits = c(-1.2, 1.2), breaks = seq(-1,1,.5)) 
```

#organize file- amygala bilateral subnuclei 
#change the data files each time to the nucleus mask you want to check: LB, CM, or SF 
```{r}
#contrast 1
  DROI_amyg_cond1 <- read.csv ("data/ROI_juelich_thr60_lbamyg_bilateral_resample_NL6Asym_cond1.csv")
  DROI_amyg_cond1$Subject <- rep(valid_subj$Subject, each=2)
  DROI_amyg_cond1$Subject <- as.numeric(gsub("sub-","",DROI_amyg_cond1$Subject))
  DROI_amyg_cond1$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_amyg_cond1 <- reshape(DROI_amyg_cond1, timevar="contrast",idvar="Subject", direction="wide")
  DROI_amyg_cond1$order <- "cond1"

#contrast 2
  DROI_amyg_cond2 <- read.csv ("data/ROI_juelich_thr60_lbamyg_bilateral_resample_NL6Asym_cond2.csv")
  DROI_amyg_cond2$Subject <- rep(valid_subj$Subject, each=2)
  DROI_amyg_cond2$Subject <- as.numeric(gsub("sub-","",DROI_amyg_cond2$Subject))
  DROI_amyg_cond2$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_amyg_cond2 <- reshape(DROI_amyg_cond2, timevar="contrast",idvar="Subject", direction="wide")
  DROI_amyg_cond2$order <- "cond2"

#combine conditions
  DROI_amyg <- rbind(DROI_amyg_cond1,DROI_amyg_cond2)

#merge with parent/alone version
  DROI_amyg <- merge(DROI_amyg,DParentInfoLong, by=c("Subject","order"), all.x=T, all.y=F)

#merge with sex and age
  DROI_amyg <- merge(DROI_amyg,DBehav_Wide[,c("Subject","SEX","MRI_AGE")],
                              by="Subject", all.x=T, all.y=F)
 
#do effect coding for categorical variables and center continuous variables
  DROI_amyg <- DROI_amyg %>%
    dplyr::mutate(SEX_effectc = ifelse(SEX=="m",-1,1),
                  Parent_Alone_effectc = ifelse(Parent_Alone=="Alone",-1,1),
                  MRI_AGE_c = scale(MRI_AGE, scale=F),
                  order_effectc = ifelse(order=="cond1",-1,1))
   
#create a wide format for later plotting and visualization purposes 
  DROI_amyg_wide <- reshape(DROI_amyg, timevar="Parent_Alone",idvar="Subject", direction="wide")
```

#test results amygdala bilateral subnuclei: US vs. baseline contrast 
```{r}
#look at the descriptive statistics
  describeBy (data= DROI_amyg, amyg_activation.noise_baseline~Parent_Alone)

#multilevel linear regression controlling for sex, age and order
 lmer_amyg_noise_baseline_sex_age_order <- lmer(data=DROI_amyg,
                                                amyg_activation.noise_baseline~ Parent_Alone_effectc*SEX_effectc + Parent_Alone_effectc*MRI_AGE_c + Parent_Alone_effectc*order_effectc +(1|Subject))
 report(lmer_amyg_noise_baseline_sex_age_order)
 
#multilevel linear regression with no covariates
 lmer_amyg_noise_baseline <- lmer(data=DROI_amyg, amyg_activation.noise_baseline~ Parent_Alone_effectc + (1|Subject))
 report(lmer_amyg_noise_baseline)
  
# since there is a significant sex X parental context interaction in the LB amygdala, examine the results separately for males and females
  describe(data = DROI_amyg, amyg_activation.noise_baseline~SEX*Parent_Alone)
  
  lmer_amyg_noise_baseline_males <-lmer(data= DROI_amyg[DROI_amyg$SEX=="m",], 
                                        amyg_activation.noise_baseline~Parent_Alone_effectc + (1|Subject))
  report(lmer_amyg_noise_baseline_males)
  
  lmer_amyg_noise_baseline_females <-lmer(data= DROI_amyg[DROI_amyg$SEX=="f",], 
                                          amyg_activation.noise_baseline~Parent_Alone_effectc + (1|Subject))
  report(lmer_amyg_noise_baseline_females)

#for visualization, mark how many subjects show decrease and how many show increase according to parental context
  DROI_amyg_wide <- DROI_amyg_wide %>%
  mutate(trend_amyg_noise = ifelse(amyg_activation.noise_baseline.Parent>amyg_activation.noise_baseline.Alone,1,
                        ifelse(amyg_activation.noise_baseline.Parent<amyg_activation.noise_baseline.Alone,-1,NA)))

  DROI_amyg <- merge(DROI_amyg,DROI_amyg_wide[,c("Subject","trend_amyg_noise")],
                              by="Subject", all.x=T, all.y=F)
  
  summary(as.factor(DROI_amyg_wide$trend_amyg_noise))

#visualize results - separate colors for participants who showed increase or decrease in parental presence vs absence
 plot_amyg_noise_baseline <- ggplot(data = DROI_amyg, 
                               aes(group=interaction(Subject,trend_amyg_noise), x=Parent_Alone,y = amyg_activation.noise_baseline, color=as.factor(trend_amyg_noise)))+
  geom_line(aes(group=interaction(Subject,trend_amyg_noise), x=Parent_Alone,y=amyg_activation.noise_baseline, color=as.factor(trend_amyg_noise)), size=1)+
   stat_summary(fun=mean,geom="line",lwd=2,color="black",aes(group=1))+
  scale_color_brewer(palette="Set2")+
  theme_classic() +
  labs (x = "", y = "Activation (US vs. baseline)", title="")+
  theme(axis.text = element_text(size = 40) , axis.title = element_text(size = 40))+
  theme(legend.position="none", plot.title = element_text(hjust = 0.5, size=50))+
  scale_x_discrete(expand = expansion(mult=c(0.4,2)), labels=c("Absence", "Presence"))+
  scale_y_continuous(limits = c(-1.2, 1.2), breaks = seq(-1,1,.5)) 
```

#test results amygdala bilateral subnuclei: CS+ vs. CS- contrast 
```{r}
#look at the descriptive statistics
  describeBy (data= DROI_amyg, amyg_activation.plus_minus~Parent_Alone)

#multilevel linear regression controlling for sex, age and order
  lmer_amyg_plus_minus_sex_age_order <- lmer(data=DROI_amyg, 
                                             amyg_activation.plus_minus~ Parent_Alone_effectc*SEX_effectc + Parent_Alone_effectc*MRI_AGE_c + Parent_Alone_effectc*order_effectc +(1|Subject))
 report(lmer_amyg_plus_minus_sex_age_order)
 
#multilevel linear regression with no covariates
 lmer_amyg_plus_minus <- lmer(data=DROI_amyg, amyg_activation.plus_minus~ Parent_Alone_effectc + (1|Subject))
 report(lmer_amyg_plus_minus)

# since there is a significant age X parental context interaction in the SF amygdala, examine the results separately for males and females
  describe(data = DROI_amyg, amyg_activation.plus_minus~SEX*Parent_Alone)
  
  lmer_amyg_plus_minus_males <-lmer(data= DROI_amyg[DROI_amyg$SEX=="m",], 
                                    amyg_activation.plus_minus~Parent_Alone_effectc + (1|Subject))
  report(lmer_amyg_plus_minus_males)
  
  lmer_amyg_plus_minus_females <-lmer(data= DROI_amyg[DROI_amyg$SEX=="f",], 
                                      amyg_activation.plus_minus~Parent_Alone_effectc + (1|Subject))
  report(lmer_amyg_plus_minus_females)
```

#make a table for automatic reporting on lmer results with age and sex variables
#change the first two lines each time to the lmer model you want to print
```{r}
  report_lmer <- as.data.frame(report(lmer_mPFC_plus_minus_sex_age_order))
  sum_lmer <- summary(lmer_mPFC_plus_minus_sex_age_order)

  lmer_table <- as.data.frame (matrix(nrow=11,ncol=2))
  colnames(lmer_table) <- c("effect","report")
  lmer_table$effect <- c("total R2","Fixed R2","Random variance","Fixed intercept","Sex","Age","Order","Parental context",
                       "Parental context X Sex", "Parental context X Age", "Parental context X Order")

  lmer_table[1,2] <- round(report_lmer$Fit[which(report_lmer$Parameter=="R2 (conditional)")],2)
  lmer_table[2,2] <- round(report_lmer$Fit[which(report_lmer$Parameter=="R2 (marginal)")],2)
  lmer_table[3,2] <- round(as.numeric(sum_lmer$varcor[1]),2)

  lmer_table[4,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="(Intercept)")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="(Intercept)")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="(Intercept)")],2),"], ", "t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="(Intercept)")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="(Intercept)")],3))

  lmer_table[5,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="SEX effectc")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="SEX effectc")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="SEX effectc")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="SEX effectc")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="SEX effectc")],3),
", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="SEX effectc")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="SEX effectc")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="SEX effectc")],2),"]")
  
  lmer_table[6,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="MRI AGE c")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="MRI AGE c")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="MRI AGE c")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="MRI AGE c")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="MRI AGE c")],3), ", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="MRI AGE c")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="MRI AGE c")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="MRI AGE c")],2),"]")
  
  lmer_table[7,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="order effectc")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="order effectc")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="order effectc")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="order effectc")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="order effectc")],3),
  ", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="order effectc")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="order effectc")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="order effectc")],2),"]")
  
  lmer_table[8,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="Parent Alone effectc")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="Parent Alone effectc")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="Parent Alone effectc")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="Parent Alone effectc")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="Parent Alone effectc")],3),
  ", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="Parent Alone effectc")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="Parent Alone effectc")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="Parent Alone effectc")],2),"]")
  
  lmer_table[9,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],3),
  ", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="Parent Alone effectc × SEX effectc")],2),"]")
  
  lmer_table[10,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],3), ",
  B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="Parent Alone effectc × MRI AGE c")],2),"]")
  
  lmer_table[11,2] <- paste0("b=",round(report_lmer$Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2)," [",
  round(report_lmer$CI_low[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2), ",",
  round(report_lmer$CI_high[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2),"], t(",
  report_lmer$df_error[1],")=",round(report_lmer$t[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2),", p=",
  round(report_lmer$p[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],3), ", B=",round(report_lmer$Std_Coefficient[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2)," [",
  round(report_lmer$Std_Coefficient_CI_low[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2), ",",
  round(report_lmer$Std_Coefficient_CI_high[which(report_lmer$Parameter=="Parent Alone effectc × order effectc")],2),"]")
  
  write.csv(lmer_table, file="lmer_table.csv")

```

#exploratory analysis- check correlations between the two contrasts of interest
```{r}
cor.test(DROI_amyg$amyg_activation.noise_baseline[DROI_amyg$Parent_Alone=="Alone"],
         DROI_amyg$amyg_activation.plus_minus[DROI_amyg$Parent_Alone=="Alone"])
cor.test(DROI_amyg$amyg_activation.noise_baseline[DROI_amyg$Parent_Alone=="Parent"],
         DROI_amyg$amyg_activation.plus_minus[DROI_amyg$Parent_Alone=="Parent"])


cor.test(DROI_mPFC$mPFC_activation.noise_baseline[DROI_amyg$Parent_Alone=="Alone"],
         DROI_mPFC$mPFC_activation.plus_minus[DROI_amyg$Parent_Alone=="Alone"])
cor.test(DROI_mPFC$mPFC_activation.noise_baseline[DROI_amyg$Parent_Alone=="Parent"],
         DROI_mPFC$mPFC_activation.plus_minus[DROI_amyg$Parent_Alone=="Parent"])

```

#control analysis- check correlations between the contrasts in the left primary motor cotext
```{r}
#contrast 1
  DROI_primotor_cond1 <- read.csv ("data/ROI_primmotor_l_-37_-25_62_resampled_NL6Asym_cond1.csv")
  DROI_primotor_cond1$Subject <- rep(valid_subj$Subject, each=2)
  DROI_primotor_cond1$Subject <- as.numeric(gsub("sub-","",DROI_primotor_cond1$Subject))
  DROI_primotor_cond1$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_primotor_cond1 <- reshape(DROI_primotor_cond1, timevar="contrast",idvar="Subject", direction="wide")
  DROI_primotor_cond1$order <- "cond1"

#contrast 2
  DROI_primotor_cond2 <- read.csv ("data/ROI_primmotor_l_-37_-25_62_resampled_NL6Asym_cond2.csv")
  DROI_primotor_cond2$Subject <- rep(valid_subj$Subject, each=2)
  DROI_primotor_cond2$Subject <- as.numeric(gsub("sub-","",DROI_primotor_cond2$Subject))
  DROI_primotor_cond2$contrast <- rep(c("noise_baseline","plus_minus"),times=nrow(valid_subj))
  DROI_primotor_cond2 <- reshape(DROI_primotor_cond2, timevar="contrast",idvar="Subject", direction="wide")
  DROI_primotor_cond2$order <- "cond2"

#combine conditions
  DROI_primotor <- rbind(DROI_primotor_cond1,DROI_primotor_cond2)

#merge with parent/alone version
  DROI_primotor <- merge(DROI_primotor,DParentInfoLong, by=c("Subject","order"), all.x=T, all.y=F)
  
#check correlation between the contrasts
  cor.test(DROI_primotor$primotor_activation.noise_baseline[DROI_primotor$Parent_Alone=="Alone"],
         DROI_primotor$primotor_activation.plus_minus[DROI_primotor$Parent_Alone=="Alone"])
  cor.test(DROI_primotor$primotor_activation.noise_baseline[DROI_primotor$Parent_Alone=="Parent"],
         DROI_primotor$primotor_activation.plus_minus[DROI_primotor$Parent_Alone=="Parent"])
```

